Matching Bullets

### 2015-12-02 imaging-paper.Rnw
fixed non CMS runs

>>>>

\begin{figure}
<<distr.dist, echo=FALSE, fig.width=7, fig.height=4, out.width='\\linewidth'>>=
ggplot(data=bstats) + 
    geom_jitter(aes(x=factor(cms), y=distr.dist, colour=match)) +
    theme(legend.position="bottom") + 
    xlab("maximum CMS")
@
\caption{If the distance between the crosscuts is small, a smaller number of CMS might already be an indication of a match.}
\end{figure}
